Software Ticket Quality

### 2017-11-25 proposal/mprop.tex
Work on study design

% \textbf{}\cite{}:
% \begin{itemize}
%   \item \textbf{What were the goals?}
%   \item \textbf{What was the method?}
%   \item \textbf{What did they learn?}
%   \item \textbf{Relevance to our work}:
% \end{itemize}

@@

>>>>

@@

In order to conduct a thorough background survey, several topics needed to be 
explored, among which the most important were:
  \begin{itemize}
    \item data quality and metrics;
    \item issue/ticket quality;
    \item waste in software projects;
    \item sentiment analysis.
  \end{itemize}

The main sources of information when searching for papers were Google Scholar, 
ACM digital library and IEEE Xplore digital library. The first step in the 
literature review process was finding relevant papers that could aid us in
our research and splitting them into the categories mentioned above. There were
a couple of key search phrases that I started with (along with slight 
variations):
  \begin{itemize}
    \item software data quality;
    \item software data quality metrics;
    \item data quality in software projects;
    \item issue quality in software projects;
    \item ticket quality software;
    \item sentiment analysis;
    \item software project communication waste.
  \end{itemize}

Then, after reading the papers retrieved when searching for the above-mentioned
phrases, I also applied the snowballing research technique as per Dr. Storer's 
advice. This extra step was helpful and allowed me to easily find linked 
papers and correlate them in this literature review.

Moreover, when reading papers, one key aspect for selecting and including it
in the literature review was citation count. Thus, after finding the most 
cited papers, I then checked to see the journal where it was published so that
we would only have material from the most important journals.

Even though the literature review contains around 40 papers, there were
around 80 papers that were reviewed but roughly half of them were excluded 
because they eventually proved to not be so relevant to our research.

Firstly, we will deal with a large volume of tickets and information extracted 
from software projects and the tools that revolve around them, such as issue 
trackers and version control systems. Thus, \emph{data quality} is an important 
topic that needed to be explored in order to infer appropriate conclusions.

As the main objective of our research is to determine what makes for a good 
quality ticket, we needed to explore what was previously done in
